Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Possibly final edited version.

\begin{document}
\title{Hadoop Image Processing Framework}
\author{\IEEEauthorblockN{Sridhar Vemula}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: sridhar.vemula@okstate.edu}
  \and
  \IEEEauthorblockN{Christopher Crick}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: chriscrick@cs.okstate.edu}
}
\maketitle
\begin{abstract}
With the rapid growth of social media, the number of images being
uploaded to the internet is exploding. Massive quantities of images
are shared through multi-platform services such as Snapchat,
Instagram, Facebook and WhatsApp; recent studies estimate that over
1.8 billion photos are uploaded every day.  However, for the most
part, applications that make use of this vast data have yet to
emerge. Most current image processing applications, designed for
small-scale, local computation, do not scale well to web-sized
problems with their large requirements for computational resources and
storage.  The emergence of processing frameworks such as the Hadoop
MapReduce\cite{dean2008} platform addresses the problem of providing
a system for computationally intensive data processing and distributed
storage. However, to learn the technical complexities of developing
useful applications using Hadoop requires a large investment of time
and experience on the part of the developer.  As such, the pool of
researchers and programmers with the varied skills to develop
applications that can use large sets of images has been limited. To
address this we have developed the Hadoop Image Processing Framework\footnote[1]{S. Vemula, C. Crick Hadoop Image Processing Framework https://github.com/okstate-robotics/hipl.git},
which provides a Hadoop-based library to support large-scale image
processing. The main aim of the framework is to allow developers of
image processing applications to leverage the Hadoop MapReduce
framework without having to master its technical details and introduce
an additional source of complexity and error into their programs.
\end{abstract}

@@

The Hadoop Image Processing Framework is largely a software
engineering platform, with the goal of hiding Hadoop's complexity
while providing users with the ability to use the system for
large-scale image processing without becoming crack Hadoop engineers.
The framework's ease of use and Java-oriented semantics will further
ease the process of creating large scale image applications and
experiments. This framework is an excellent tool for novice Hadoop
users, image application developers and computer vision researchers,
allowing the rapid development of image software that can take
advantage of the huge data stores, rich metadata and global reach of
current online image sources.

@@

\section{Related Work}
With the rapid usage increase of online photo storage and social media
on sites like Facebook, Flickr and Picasa, more image data is
available than ever before, and is growing every day.  Every minute
27800 photos are uploaded to Instagram, \cite{Horaczek2013}while Facebook receives
208,300 photos over the same time frame. This alone
provides a source of image data that can scale into the billions.  The
explosion of available images on social media has motivated image
processing research and application development that can take
advantage of very large image data stores.

White et.al \cite{White2010} presents a case study of classifying and clustering billions of regular images using MapReduce. It describes an image pre-processing technique for use in a sliding-window approach for object recognition. Pereira et.al \cite{Pereira2010} outlines some of the limitations of the MapReduce model when dealing with high-speed video encoding, namely its dependence on the NameNode as a single point of failure, and lack of possibility for generalization in order to suit the issue at hand. An alternate optimized implementation is proposed for providing cloud-based IaaS (Infrastructure as a Service) solution.  Zhenhua Lv et.al \cite{Lv2010} describe using the k-means algorithm in conjunction with MapReduce and satellite/aerophoto images in order to find different elements based on their color.

Zhang et.al \cite{Zhang2010} present methods used for processing sequences of microscope images of live cells. The images are relatively small 512x512 16-bit pixels, stored in 90 MB folders there were some issues regarding to fitting into Hadoop DFS blocks with were solved by custom InputFormat, InputSplit and RecordReader classes. Mark Powell et.al \cite{Powell2010} describes the way NASA handles image processing of celestial images captured by the Mars Orbiter and rovers. Clear and concise descriptions are provided about the segmentation of gigapixel images into tiles, how the tiles are processed and how image processing framework handles scaling and works with the distributed processing. Wang, Yinhai and McCleary\cite{Wang2011} about the speeding up the analysis of Tissue MicroArray images by substituting human expert analysis for automated processing algorithms. While the images were measured to be in gigapixels, the content is easily segmented and there was no need to focus on being able to analyze all of image at once. The work was all done on a specially build grip high performance	computing platform on Hadoop framework.

Bajcsy et.al \cite{Bajcsy2013} present a characterization of four basic terabyte size image computations on a Hadoop Cluster in terms of their relative efficiency according to the modified Amdahls law. The work is motivated by the fact that there is a lack of 6 standard benchmarks and stress tests for big image processing operations on Hadoop framework. Moise et.al \cite{Moise2013} outlines about querying thousands of images in one run using Hadoop MapReduce framework using the MapReduced based eCP Algorithm. The experiment does an image search on 110 million images collected from web on Grid 5000 Platform. The results are evaluated in order to understand the best practices that can tune Hadoop MapReduce Performance for image search.

While the above shows that there has been lot of work in this area, providing a framework to ease the process develop large-scale image processing applications. The question remains how the performance for Hadoop can be increased for large scale image processing tasks on small files.

>>>>

\begin{document}
\title{Hadoop Image Processing Framework}
\author{\IEEEauthorblockN{Sridhar Vemula}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: sridhar.vemula@okstate.edu}
  \and
  \IEEEauthorblockN{Christopher Crick}
  \IEEEauthorblockA{Computer Science Department\\
    Oklahoma State University\\
    Stillwater, Oklahoma \\
    Email: chriscrick@cs.okstate.edu}
}
\maketitle
\begin{abstract}
With the rapid growth of social media, the number of images being
uploaded to the internet is exploding. Massive quantities of images
are shared through multi-platform services such as Snapchat,
Instagram, Facebook and WhatsApp; recent studies estimate that over
1.8 billion photos are uploaded every day.  However, for the most
part, applications that make use of this vast data have yet to
emerge. Most current image processing applications, designed for
small-scale, local computation, do not scale well to web-sized
problems with their large requirements for computational resources and
storage.  The emergence of processing frameworks such as the Hadoop
MapReduce\cite{dean2008} platform addresses the problem of providing
a system for computationally intensive data processing and distributed
storage. However, to learn the technical complexities of developing
useful applications using Hadoop requires a large investment of time
and experience on the part of the developer.  As such, the pool of
researchers and programmers with the varied skills to develop
applications that can use large sets of images has been limited. To
address this we have developed the Hadoop Image Processing Framework,
which provides a Hadoop-based library to support large-scale image
processing. The main aim of the framework is to allow developers of
image processing applications to leverage the Hadoop MapReduce
framework without having to master its technical details and introduce
an additional source of complexity and error into their programs.
\end{abstract}

@@

The Hadoop Image Processing Framework is largely a software
engineering platform, with the goal of hiding Hadoop's complexity
while providing users with the ability to use the system for
large-scale image processing without becoming crack Hadoop engineers.
The framework's ease of use and Java-oriented semantics will further
ease the process of creating large scale image applications and
experiments. This framework is an excellent tool for novice Hadoop
users, image application developers and computer vision researchers,
allowing the rapid development of image software that can take
advantage of the huge data stores, rich metadata and global reach of
current online image sources.\footnote[1]{The Hadoop Image Processing
  Framework is open source and freely available for download at
  https://github.com/okstate-robotics/hipl.git}.

@@

\section{Related Work}
With the rapid usage increase of online photo storage and social media
on sites like Facebook, Flickr and Picasa, more image data is
available than ever before, and is growing every day.  Every minute
27,800 photos are uploaded to Instagram,\cite{Horaczek2013} while
Facebook receives 208,300 photos over the same time frame. This alone
provides a source of image data that can scale into the billions.  The
explosion of available images on social media has motivated image
processing research and application development that can take
advantage of very large image data stores.

White et.al \cite{White2010} presents a case study of classifying and
clustering billions of regular images using MapReduce.  It describes
an image pre-processing technique for use in a sliding-window approach
for object recognition.  Pereira et.al \cite{Pereira2010} outlines
some of the limitations of the MapReduce model when dealing with
high-speed video encoding, namely its dependence on the NameNode as a
single point of failure, and the difficulties inherent in generalizing
the framework to suit particular issues.  It proposes an alternate
optimized implementation for providing cloud-based IaaS
(Infrastructure as a Service) solutions.  Lv et.al \cite{Lv2010}
describes using the $k$-means algorithm in conjunction with MapReduce
and satellite/aerial photographs in order to find different elements
based on their color.

Zhang et.al \cite{Zhang2010} presents methods used for processing
sequences of microscope images of live cells. The images are
relatively small (512x512, 16-bit pixels).  Stored in 90 MB folders,
the authors encountered difficulties regarding fitting into Hadoop DFS
blocks with were solved by custom InputFormat, InputSplit and
RecordReader classes.  Powell et.al \cite{Powell2010} describes how
NASA handles image processing of celestial images captured by the Mars
Orbiter and rovers. Clear and concise descriptions are provided about
the segmentation of gigapixel images into tiles, how the tiles are
processed and how the image processing framework handles scaling and
works with the distributed processing. Wang, Yinhai and
McCleary\cite{Wang2011} discuss speeding up the analysis of tissue
microarray images by substituting human expert analysis for automated
processing algorithms. While the images were gigapixel-sized, the
content was easily segmented and there was no need to analyze all of
an image at once. The work was all done on a specially-built high
performance computing platform using the Hadoop framework.

Bajcsy et.al \cite{Bajcsy2013} present a characterization of four
basic terabyte-size image computations on a Hadoop cluster in terms of
their relative efficiency according to a modified Amdahl's Law. The
work was motivated by the fact that there is a lack of standard
benchmarks and stress tests for large-scale image processing
operations on the Hadoop framework. Moise et.al \cite{Moise2013}
outlines the querying of thousands of images in one run using the
Hadoop MapReduce framework and the eCP Algorithm. The experiment
performs an image search on 110 million images collected from the web
using the Grid 5000 platform. The results are evaluated in order to
understand the best practices for tuning Hadoop MapReduce performance
for image search.

The above shows that there has been a great deal of intensive work in
image processing using MapReduce.  However, each independent project
requires a complex, error-prone, one-off implementation.  Such
research and application development would benefit greatly from a
standard, well-engineered image processing framework such as the one
we provide.
